Current state and prospects of R-packages for the design of experiments

### 2022-12-14 paper.Rmd
fixed reference name

The remainder of this paper is organized as follows. `r secref("data", "data")` briefly describes the data source used for the analysis; `r secref("eda", "Exploratory data analysis" )` presents some insights into the state of the current DoE packages by the exploratory data analysis of package download data, text descriptions and comparisons with other CRAN task views; `r secref("design", "Interface design")` discusses the interface designs of widely used DoE packages, and we conclude with a discussion in `r secref("discussion", "Discussion")` of future prospects in the software development of experimental designs.

>>>>

The remainder of this paper is organized as follows. `r secref("data", "Data")` briefly describes the data source used for the analysis; `r secref("eda", "Exploratory data analysis" )` presents some insights into the state of the current DoE packages by the exploratory data analysis of package download data, text descriptions and comparisons with other CRAN task views; `r secref("design", "Interface design")` discusses the interface designs of widely used DoE packages, and we conclude with a discussion in `r secref("discussion", "Discussion")` of future prospects in the software development of experimental designs.
